Brownian Dynein Model

### 2015-09-16 latex/derivation.tex
Add changes to bothbound solution.

\begin{align}
  X_{nm} &= L_{s}*((\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}})(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}) - \sqrt{1-(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}})^2}\sqrt{1-(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}})^2}) \\
  Y_{nm} &= L_{s}*(\sqrt{1-(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}})^2}(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}})+(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}})\sqrt{1-(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}})^2}) \\
\end{align}

\section{Cartesian from Angular Coordinates}
This section lays out the definitions of the coordinates of the Dynein model. \\
\begin{align}
  X_{b1} &= 0 \\
  X_{m1} &= L_{s}*\cos(\Theta_{b1}) \\
  X_{t}  &= ?? \\
  X_{m2} &= L_{s}*\cos(\Theta_{b2}) \\
  X_{b2} &= L \\
\end{align}

\begin{align}
  Y_{b1} &= 0 \\
  Y_{m1} &= L_{s}*\sin(\Theta_{b1}) \\
  Y_{t}  &= ?? \\
  Y_{m2} &= L_{s}*\sin(\Theta_{b2}) \\
  Y_{b2} &= 0
\end{align}

\section{Cartesian Velocities}
This section shows the velocity definitions. \\
\begin{align}
  \dot{X}_{b1} &= 0 \\
  \dot{X}_{m1} &= -L_{s}*\sin(\Theta_{b1})*\dot{\Theta}_{b1} \\
  \dot{X}_{t } &= ?? \\
  \dot{X}_{m2} &= -L_{s}*\sin(\Theta_{b2})*\dot{\Theta}_{b2} \\
  \dot{X}_{b2} &= 0
\end{align}

\begin{align}                                                                          
  \dot{Y}_{b1} &= 0 \\                                         
  \dot{Y}_{m1} &= L_{s}*\cos(\Theta_{b1})*\dot{\Theta}_{b1} \\
  \dot{Y}_{t}  &= ?? \\
  \dot{Y}_{m2} &= L_{s}*\cos(\Theta_{b2})*\dot{\Theta}_{b2} \\
  \dot{Y}_{b2} &= 0 \\
\end{align}

\section{Brownian Equations}
This section shows the velocity definitions using the Brownian dynamics equation. \\
\begin{align}  
  \dot{X}_{b1} &= 0 \\
  \dot{X}_{m1} &= \frac{1}{\gamma} \Big(F_{xml} + \mn \lambda_{bs}(X_{m1} - X_{b1}) + \lambda_{bt}(X_{t } - X_{m1}) \Big) + R_{xml} \\
  \dot{X}_{t } &= \frac{1}{\gamma} \Big(F_{xt } + \mn \lambda_{bt}(X_{t } - X_{m1}) + \lambda_{bt}(X_{m2} - X_{t }) \Big) + R_{xt } \\
  \dot{X}_{m2} &= \frac{1}{\gamma} \Big(F_{xmr} + \mn \lambda_{bt}(X_{m2} - X_{t }) + \lambda_{fs}(X_{b2} - X_{m2}) \Big) + R_{xmr} \\
  \dot{X}_{b2} &= \frac{1}{\gamma} \Big(F_{xbr} + \mn \lambda_{fs}(X_{b2} - X_{m2})                                 \Big) + R_{xbr}
\end{align}

\begin{align}  
  \dot{Y}_{b1} &= 0 \\
  \dot{Y}_{m1} &= \frac{1}{\gamma} \Big(F_{yml} + \mn \lambda_{bs}(Y_{m1} - Y_{b1}) + \lambda_{bt}(Y_{t } - Y_{m1}) \Big) + R_{yml} \\
  \dot{Y}_{t}  &= \frac{1}{\gamma} \Big(F_{yt } + \mn \lambda_{bt}(Y_{t } - Y_{m1}) + \lambda_{bt}(Y_{m2} - Y_{t }) \Big) + R_{yt } \\
  \dot{Y}_{m2} &= \frac{1}{\gamma} \Big(F_{ymr} + \mn \lambda_{bt}(Y_{m2} - Y_{t }) + \lambda_{fs}(Y_{b2} - Y_{m2}) \Big) + R_{ymr} \\
  \dot{Y}_{b2} &= \frac{1}{\gamma} \Big(F_{ybr} + \mn \lambda_{fs}(Y_{b2} - Y_{m2})                                 \Big) + R_{ybr}
\end{align}

@@

\begin{align}  
  \dot{X}_{m1} &= \dot{X}_{b1} + \mn L_{s}\sin(\Theta_{b1})\dot{\Theta}_{b1} = \frac{1}{\gamma}F_{xml} + \mn\frac{1}{\gamma}\lambda_{bs}(X_{m1} - X_{b1}) + \frac{1}{\gamma}\lambda_{bt}(X_{t } - X_{m1}) + R_{xml} \\
  \dot{X}_{t}  &= \dot{X}_{m1} + \mn L_{t}\sin(\Theta_{m1})\dot{\Theta}_{m1} = \frac{1}{\gamma}F_{xt } + \mn\frac{1}{\gamma}\lambda_{bt}(X_{t } - X_{m1}) + \frac{1}{\gamma}\lambda_{bt}(X_{m2} - X_{t }) + R_{xt } \\
  \dot{X}_{m2} &= \dot{X}_{t } + L_{t}\sin(\Theta_{m2})\dot{\Theta}_{m2} = \frac{1}{\gamma}F_{xmr} + \mn\frac{1}{\gamma}\lambda_{bt}(X_{m2} - X_{t }) + \frac{1}{\gamma}\lambda_{fs}(X_{b2} - X_{m2}) + R_{xmr} \\
  \dot{X}_{b2} &= \dot{X}_{m2} + L_{s}\sin(\Theta_{b2})\dot{\Theta}_{b2} = \frac{1}{\gamma}F_{xbr} + \mn\frac{1}{\gamma}\lambda_{fs}(X_{b2} - X_{m2}) + R_{xbr}
\end{align}

\begin{align}  
  \dot{Y}_{m1} &= \dot{Y}_{b1} + L_{s}\cos(\Theta_{b1})\dot{\Theta}_{b1} = \frac{1}{\gamma}F_{yml} + \mn\frac{1}{\gamma}\lambda_{bs}(Y_{m1} - Y_{b1}) + \frac{1}{\gamma}\lambda_{bt}(Y_{t } - Y_{m1}) + R_{yml} \\
  \dot{Y}_{t}  &= \dot{Y}_{m1} + L_{t}\cos(\Theta_{m1})\dot{\Theta}_{m1} = \frac{1}{\gamma}F_{yt } + \mn\frac{1}{\gamma}\lambda_{bt}(Y_{t } - Y_{m1}) + \frac{1}{\gamma}\lambda_{bt}(Y_{m2} - Y_{t }) + R_{yt } \\
  \dot{Y}_{m2} &= \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{m2})\dot{\Theta}_{m2} = \frac{1}{\gamma}F_{ymr} + \mn\frac{1}{\gamma}\lambda_{bt}(Y_{m2} - Y_{t }) + \frac{1}{\gamma}\lambda_{fs}(Y_{b2} - Y_{m2}) + R_{ymr} \\
  \dot{Y}_{b2} &= \dot{Y}_{m2} + \mn L_{s}\cos(\Theta_{b2})\dot{\Theta}_{b2} = \frac{1}{\gamma}F_{ybr} + \mn\frac{1}{\gamma}\lambda_{fs}(Y_{b2} - Y_{m2}) + R_{ybr}
\end{align}

@@

\begin{multline}
\mn\frac{1}{\gamma}\lambda_{bs}(X_{m1} - X_{b1}) =
\dot{X}_{b1} + \mn L_{s}\sin(\Theta_{b1})\dot{\Theta}_{b1} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{m1} + \mn L_{t}\sin(\Theta_{m1})\dot{\Theta}_{m1} - R_{xt } \\
- \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{m2})\dot{\Theta}_{m2} - R_{xmr}
-\frac{1}{\gamma}F_{xmr} + \dot{X}_{m2} + L_{s}\sin(\Theta_{b2})\dot{\Theta}_{b2} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
\label{eq:Ax}
\end{multline}%Fix'd

\begin{multline}
\mn\frac{1}{\gamma}\lambda_{bt}(X_{t } - X_{m1}) =
\dot{X}_{m1} + \mn L_{t}\sin(\Theta_{m1})\dot{\Theta}_{m1} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{m2})\dot{\Theta}_{m2} \\
- R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{m2} + L_{s}\sin(\Theta_{b2})\dot{\Theta}_{b2} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
\label{eq:Bx}
\end{multline}%Fix'd

\begin{equation}
\mn\frac{1}{\gamma}\lambda_{bt}(X_{m2} - X_{t }) =
\dot{X}_{t } + L_{t}\sin(\Theta_{m2})\dot{\Theta}_{m2} - R_{xmr} - \frac{1}{\gamma}F_{xmr}
+ \dot{X}_{m2} + L_{s}\sin(\Theta_{b2})\dot{\Theta}_{b2} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
\label{eq:Cx}
\end{equation}%Fix'd

\begin{equation}
\mn\frac{1}{\gamma}\lambda_{fs}(X_{b2} - X_{m2}) = 
\dot{X}_{m2} + L_{s}\sin(\Theta_{b2})\dot{\Theta}_{b2} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
\label{eq:Dx}
\end{equation}%Fix'd

\begin{multline}
\mn\frac{1}{\gamma}\lambda_{bs}(Y_{m1} - Y_{b1}) =
\dot{Y}_{b1} + L_{s}\cos(\Theta_{b1})\dot{\Theta}_{b1} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{m1} + L_{t}\cos(\Theta_{m1})\dot{\Theta}_{m1} \\
- R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{m2})\dot{\Theta}_{m2} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{m2}
+ \mn L_{s}\cos(\Theta_{b2})\dot{\Theta}_{b2} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
\label{eq:Ay}
\end{multline}%Fix'd

\begin{multline}
\mn\frac{1}{\gamma}\lambda_{bt}(Y_{t } - Y_{m1}) =
\dot{Y}_{m1} + L_{t}\cos(\Theta_{m1})\dot{\Theta}_{m1} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{m2})\dot{\Theta}_{m2} \\
- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{m2} + \mn L_{s}\cos(\Theta_{b2})\dot{\Theta}_{b2} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
\label{eq:By}
\end{multline}%Fix'd

\begin{equation}
\mn\frac{1}{\gamma}\lambda_{bt}(Y_{m2} - Y_{t }) =
\dot{Y}_{t } + \mn L_{t}\cos(\Theta_{m2})\dot{\Theta}_{m2} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{m2} + \mn L_{s}\cos(\Theta_{b2})\dot{\Theta}_{b2}
- R_{ybr} - \frac{1}{\gamma}F_{ybr}
\label{eq:Cy}
\end{equation}%Fix'd

\begin{equation}
\mn\frac{1}{\gamma}\lambda_{fs}(Y_{b2} - Y_{m2}) = \dot{Y}_{m2} + \mn L_{s}\cos(\Theta_{b2})\dot{\Theta}_{b2} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
\label{eq:Dy}
\end{equation}%Fix'd

>>>>

\begin{align}
  X_{nm} &= L_{s}\Bigg( \Big(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\Big)\Big(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\Big) - \sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2} \Bigg) \\
  Y_{nm} &= L_{s}\Bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2}+\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2} \Bigg) \\
\end{align}

\section{Cartesian from Angular Coordinates}
This section lays out the definitions of the coordinates of the Dynein model. \\
\begin{align}
  X_{nb} &= 0 \\
  X_{nm} &= L_{s}*\cos(\Theta_{nb}) \\
  X_{t}  &= ?? \\
  X_{fm} &= L_{s}*\cos(\Theta_{fb}) \\
  X_{fb} &= L \\
\end{align}

\begin{align}
  Y_{nb} &= 0 \\
  Y_{nm} &= L_{s}*\sin(\Theta_{nb}) \\
  Y_{t}  &= ?? \\
  Y_{fm} &= L_{s}*\sin(\Theta_{fb}) \\
  Y_{fb} &= 0
\end{align}

\section{Cartesian Velocities}
This section shows the velocity definitions. \\
\begin{align}
  \dot{X}_{nb} &= 0 \\
  \dot{X}_{nm} &= -L_{s}*\sin(\Theta_{nb})*\dot{\Theta}_{nb} \\
  \dot{X}_{t } &= ?? \\
  \dot{X}_{fm} &= -L_{s}*\sin(\Theta_{fb})*\dot{\Theta}_{fb} \\
  \dot{X}_{fb} &= 0
\end{align}

\begin{align}                                                                          
  \dot{Y}_{nb} &= 0 \\                                         
  \dot{Y}_{nm} &= L_{s}*\cos(\Theta_{nb})*\dot{\Theta}_{nb} \\
  \dot{Y}_{t}  &= ?? \\
  \dot{Y}_{fm} &= L_{s}*\cos(\Theta_{fb})*\dot{\Theta}_{fb} \\
  \dot{Y}_{fb} &= 0 \\
\end{align}

\section{Brownian Equations}
This section shows the velocity definitions using the Brownian dynamics equation. \\
\begin{align}  
  \dot{X}_{nb} &= 0 \\
  \dot{X}_{nm} &= \frac{1}{\gamma} \Big(F_{xml} + \mn \lambda_{bs}(X_{nm} - X_{nb}) + \lambda_{bt}(X_{t } - X_{nm}) \Big) + R_{xml} \\
  \dot{X}_{t } &= \frac{1}{\gamma} \Big(F_{xt } + \mn \lambda_{bt}(X_{t } - X_{nm}) + \lambda_{bt}(X_{fm} - X_{t }) \Big) + R_{xt } \\
  \dot{X}_{fm} &= \frac{1}{\gamma} \Big(F_{xmr} + \mn \lambda_{bt}(X_{fm} - X_{t }) + \lambda_{fs}(X_{fb} - X_{fm}) \Big) + R_{xmr} \\
  \dot{X}_{fb} &= \frac{1}{\gamma} \Big(F_{xbr} + \mn \lambda_{fs}(X_{fb} - X_{fm})                                 \Big) + R_{xbr}
\end{align}

\begin{align}  
  \dot{Y}_{nb} &= 0 \\
  \dot{Y}_{nm} &= \frac{1}{\gamma} \Big(F_{yml} + \mn \lambda_{bs}(Y_{nm} - Y_{nb}) + \lambda_{bt}(Y_{t } - Y_{nm}) \Big) + R_{yml} \\
  \dot{Y}_{t}  &= \frac{1}{\gamma} \Big(F_{yt } + \mn \lambda_{bt}(Y_{t } - Y_{nm}) + \lambda_{bt}(Y_{fm} - Y_{t }) \Big) + R_{yt } \\
  \dot{Y}_{fm} &= \frac{1}{\gamma} \Big(F_{ymr} + \mn \lambda_{bt}(Y_{fm} - Y_{t }) + \lambda_{fs}(Y_{fb} - Y_{fm}) \Big) + R_{ymr} \\
  \dot{Y}_{fb} &= \frac{1}{\gamma} \Big(F_{ybr} + \mn \lambda_{fs}(Y_{fb} - Y_{fm})                                 \Big) + R_{ybr}
\end{align}

@@

\begin{align}  
  \dot{X}_{nm} &= \dot{X}_{nb} + \mn L_{s}\sin(\Theta_{nb})\dot{\Theta}_{nb} = \frac{1}{\gamma}F_{xml} + \mn\frac{1}{\gamma}\lambda_{bs}(X_{nm} - X_{nb}) + \frac{1}{\gamma}\lambda_{bt}(X_{t } - X_{nm}) + R_{xml} \\
  \dot{X}_{t}  &= \dot{X}_{nm} + \mn L_{t}\sin(\Theta_{nm})\dot{\Theta}_{nm} = \frac{1}{\gamma}F_{xt } + \mn\frac{1}{\gamma}\lambda_{bt}(X_{t } - X_{nm}) + \frac{1}{\gamma}\lambda_{bt}(X_{fm} - X_{t }) + R_{xt } \\
  \dot{X}_{fm} &= \dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} = \frac{1}{\gamma}F_{xmr} + \mn\frac{1}{\gamma}\lambda_{bt}(X_{fm} - X_{t }) + \frac{1}{\gamma}\lambda_{fs}(X_{fb} - X_{fm}) + R_{xmr} \\
  \dot{X}_{fb} &= \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} = \frac{1}{\gamma}F_{xbr} + \mn\frac{1}{\gamma}\lambda_{fs}(X_{fb} - X_{fm}) + R_{xbr}
\end{align}

\begin{align}  
  \dot{Y}_{nm} &= \dot{Y}_{nb} + L_{s}\cos(\Theta_{nb})\dot{\Theta}_{nb} = \frac{1}{\gamma}F_{yml} + \mn\frac{1}{\gamma}\lambda_{bs}(Y_{nm} - Y_{nb}) + \frac{1}{\gamma}\lambda_{bt}(Y_{t } - Y_{nm}) + R_{yml} \\
  \dot{Y}_{t}  &= \dot{Y}_{nm} + L_{t}\cos(\Theta_{nm})\dot{\Theta}_{nm} = \frac{1}{\gamma}F_{yt } + \mn\frac{1}{\gamma}\lambda_{bt}(Y_{t } - Y_{nm}) + \frac{1}{\gamma}\lambda_{bt}(Y_{fm} - Y_{t }) + R_{yt } \\
  \dot{Y}_{fm} &= \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} = \frac{1}{\gamma}F_{ymr} + \mn\frac{1}{\gamma}\lambda_{bt}(Y_{fm} - Y_{t }) + \frac{1}{\gamma}\lambda_{fs}(Y_{fb} - Y_{fm}) + R_{ymr} \\
  \dot{Y}_{fb} &= \dot{Y}_{fm} + \mn L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} = \frac{1}{\gamma}F_{ybr} + \mn\frac{1}{\gamma}\lambda_{fs}(Y_{fb} - Y_{fm}) + R_{ybr}
\end{align}

@@

\begin{multline}
\mn\frac{1}{\gamma}\lambda_{bs}(X_{nm} - X_{nb}) =
\dot{X}_{nb} + \mn L_{s}\sin(\Theta_{nb})\dot{\Theta}_{nb} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{nm} + \mn L_{t}\sin(\Theta_{nm})\dot{\Theta}_{nm} - R_{xt } \\
- \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} - R_{xmr}
-\frac{1}{\gamma}F_{xmr} + \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
\label{eq:Ax}
\end{multline}%Fix'd

\begin{multline}
\mn\frac{1}{\gamma}\lambda_{bt}(X_{t } - X_{nm}) =
\dot{X}_{nm} + \mn L_{t}\sin(\Theta_{nm})\dot{\Theta}_{nm} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} \\
- R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
\label{eq:Bx}
\end{multline}%Fix'd

\begin{equation}
\mn\frac{1}{\gamma}\lambda_{bt}(X_{fm} - X_{t }) =
\dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} - R_{xmr} - \frac{1}{\gamma}F_{xmr}
+ \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
\label{eq:Cx}
\end{equation}%Fix'd

\begin{multline}
\mn\frac{1}{\gamma}\lambda_{bs}(Y_{nm} - Y_{nb}) =
\dot{Y}_{nb} + L_{s}\cos(\Theta_{nb})\dot{\Theta}_{nb} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{nm} + L_{t}\cos(\Theta_{nm})\dot{\Theta}_{nm} \\
- R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{fm}
+ \mn L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
\label{eq:Ay}
\end{multline}%Fix'd

\begin{multline}
\mn\frac{1}{\gamma}\lambda_{bt}(Y_{t } - Y_{nm}) =
\dot{Y}_{nm} + L_{t}\cos(\Theta_{nm})\dot{\Theta}_{nm} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} \\
- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{fm} + \mn L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
\label{eq:By}
\end{multline}%Fix'd

\begin{equation}
\mn\frac{1}{\gamma}\lambda_{bt}(Y_{fm} - Y_{t }) =
\dot{Y}_{t } + \mn L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{fm} + \mn L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb}
- R_{ybr} - \frac{1}{\gamma}F_{ybr}
\label{eq:Cy}
\end{equation}%Fix'd
